Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations

### 2018-01-14 Analysis/RSV.Rmd
Abstract sections; inline figures using TikZ; refactoring

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")

>>>>

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")

### 2018-01-14 Thesis/Thesis.rnw
Abstract sections; inline figures using TikZ; refactoring

<<options, echo=FALSE>>=
    opts_chunk$set(echo=FALSE, message=FALSE)
@

<<load>>=
read_chunk("../Analysis/RSV.R")
@

@@

<<util>>=
library(grid)

# Formatting utilities
formatDate = function(date) {
    format(date, "%B, %d, %Y")
}

formatYear = function(date) {
    format(date, "%Y")
}

formatThreshold = function(threshold) {
    sprintf("%.2f", threshold %% 52)
}

regionOnset = function(c) {
    formatThreshold((thresholdsByCounty %>% filter(county==c))$onset.median)
}

regionOffset = function(c) {
    formatThreshold((thresholdsByCounty %>% filter(county==c))$offset.median)
}

formatThresholdCI = function(lower, upper, level) {
    sprintf("%d\\%% CI: %.2f -- %.2f", level * 100, lower %% 52, upper %% 52)
}

regionOnsetCI = function(c, level) {
    formatThresholdCI(
        (thresholdsByCounty %>% filter(county==c))$onset.lower, 
        (thresholdsByCounty %>% filter(county==c))$onset.upper, 
        level
    )
}

regionOffsetCI = function(c, level) {
    formatThresholdCI(
        (thresholdsByCounty %>% filter(county==c))$offset.lower, 
        (thresholdsByCounty %>% filter(county==c))$offset.upper, 
        level
    )
}

formatPct = function(pct) {
    sprintf("%.2f\\%%", pct * 100)
}

formatPctCI = function(lower, upper, level) {
    sprintf("%d\\%% CI: %.2f -- %.2f\\%%", level * 100, lower * 100, upper * 100)
}

regionStrategyCoverage = function(c, s) {
    formatPct((unprotectedByCounty %>% filter(county==c, strat==s))$frac.median)
}

regionStrategyCoverageCI = function(c, s, level) {
    formatPctCI(
        (unprotectedByCounty %>% filter(county==c, strat==s))$frac.upper,
        (unprotectedByCounty %>% filter(county==c, strat==s))$frac.lower,
        level
    )
}

driftYearToWeek = function(year, negate) {
    drift = 365 / 7 * year
    if (negate) {
        -drift
    } else {
        drift
    }
}

formatDrift = function(lm, negate=FALSE) {
    sprintf("%.2f weeks", driftYearToWeek(summary(lm)$coefficients['year', 1], negate))
}

formatDriftCI = function(lm, level, negate=TRUE) {
    ci = confint(lm, "year", level=level)
    sprintf(
        "%d\\%% CI: %.2f -- %.2f weeks", level * 100, 
        driftYearToWeek(min(ci), negate), 
        driftYearToWeek(max(ci), negate)
    )
}

# Counties which we plot (so, not individual low-incidence counties)
countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]
@

\documentclass[10pt, a4paper, twocolumn]{article}
\input{structure.tex}

\usepackage{float}
\usepackage{hyperref}
\usepackage{draftwatermark}
\SetWatermarkText{DRAFT \#1}
\SetWatermarkScale{1}

\newcommand{\abstractsection}[1]{\section*{#1}}

\title{Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations}

\author{
	\authorstyle{Ben Artin\textsuperscript{1}} % Authors
	\newline\newline
	\authorstyle{Daniel Weinberger, PhD\textsuperscript{2}, advisor}\\
	\authorstyle{Virginia Pitzer, ScD\textsuperscript{2}, advisor}
	\newline\newline
	\textsuperscript{1}\institution{Yale University, School of Public Health and School of Medicine}\\
	\textsuperscript{2}\institution{Yale University, School of Public Health}
}

\date{Draft \#1, \today}

@@

@@

\clearpage

@@

\abstractsection{Background}

Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants. Immunoprophylaxis (palivizumab) is available, but costly. The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season. Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunprophylaxis regimen outside of Florida.

\abstractsection{Methods}

We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines. We also formulate several alternate immunoprophylaxis regimens with the same net pharmaceutical cost, estimate the fraction preventable by those alternate regimens.

\abstractsection{Results}

At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions. We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens. Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% state-wide increase in RSV prophylaxis coverage over the AAP regimen.

\abstractsection{Conclusion}

We conclude that the increased prophylaxis coverage provided by regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost. Our temporal analysis at the annual level showed no additional benefit beyond the spatial analysis, while simultaneously increasing implementation complexity. Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.

@@

\clearpage

%\begin{multicols}{2}

@@

\section{Data normalization}

@@

\subsection{RSV season in Fairfield county begins early and ends late}

@@

\begin{figure*}[t]
<<seasonByRegion>>=
    onset = ggplot(thresholdsByCounty %>% filter(county %in% countiesForPlots)) +
        geom_errorbarh(aes(x=onset.median, xmin=onset.lower, xmax=onset.upper, y=county), height=.25) + 
        labs(x="Season onset") +
        theme(
            axis.title.y=element_blank(),
            axis.ticks.y=element_blank()
        )
    offset = ggplot(thresholdsByCounty %>% filter(county %in% countiesForPlots)) +
        geom_errorbarh(aes(x=offset.median, xmin=offset.lower, xmax=offset.upper, y=county), height=.25) + 
        labs(x="Season offset", y=NULL) +
        theme(
            axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.ticks.y=element_blank()
        )

    ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
@
\caption{Onset and offset of RSV season in Connecticut by region}
\label{fig:seasonByRegion}
\end{figure*}

\begin{figure*}[t]
<<coverageByRegionAAP>>=
    ggplot(unprotectedByCounty %>% filter(strat=="aap") %>% filter(county %in% countiesForPlots)) +
        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.25) + 
        geom_point(aes(y=frac.median, x=county)) + 
        scale_y_continuous(labels=scales::percent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        labs(y="RSV cases occurring during prophylaxis timeframe, %") +
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank()
        )
@
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region.}
\label{fig:coverageByRegionAAP}
\end{figure*}

\begin{figure*}[t]
<<coverageByRegionAAPInsight>>=
    ggplot2.multiplot(plotlist=lapply(countiesForPlots, function(c) {
        strat = ppxFixedStrategies("all")[["aap"]]

@@

        plot = ggplot(countyPred) +
            geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25))
        plot = plot %>%
            annotation_timespan(ppxStart, ppxEnd, 1.05, hsv(1/3, 1, .5), "Prophylaxis") %>%
            annotation_timespan(countyThresholds$onset.median, countyThresholds$offset.median, -0.05, hsv(0, 1, .5), "RSV Season")
        plot = plot + 
            annotate("segment", x=-Inf, y=unprotectedAtStart, xend=ppxStart, yend=unprotectedAtStart, linetype=3) + 
            annotate("segment", x=-Inf, y=unprotectedAtEnd, xend=ppxEnd, yend=unprotectedAtEnd, linetype=3) + 
            scale_y_continuous(labels=scales::percent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.2, 0)) +
            labs(x=c) +
            theme(
                axis.title.y=element_blank(),
                axis.ticks.x=element_blank()
            )
        table = ggplot_gtable(ggplot_build(plot))
        table$layout$clip[table$layout$name == "panel"] <- "off"

        plot
    }), cols=2)
@
\caption{RSV relative cumulative incidence by region}
\label{fig:coverageByRegionAAPInsight}
\end{figure*}

\begin{figure*}[t]
<<coverageByRegion, warning=FALSE>>=
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots)
    ggplot(data) +
        scale_y_continuous(labels=scales::percent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_linetype_manual(values=c(1, 3, 4, 2, 3, 4, 2)) + 
        scale_color_manual(values=c(grey(0), rep(hsv(0, 1, 1), 3), rep(hsv(4/6, 1, 1), 3))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, linetype=strat, color=strat, group=strat), 
            width=0, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5)) +
        geom_point(aes(y=frac.lower, x=county, color=strat), position=position_dodge(.5), shape=18) +
        geom_point(aes(y=frac.upper, x=county, color=strat), position=position_dodge(.5), shape=18) +
        labs(y="RSV cases occurring during prophylaxis timeframe, %") +
        guides(color=guide_legend(keywidth=3, keyheight=1), linetype=guide_legend(keywidth=3, keyheight=1)) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank()
        )
@

\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen.}
\label{fig:coverageByRegion}
\end{figure*}

\begin{figure*}[t]
<<onsetOffsetByYear, warning=FALSE>>=
    onset = ggplot(stateThresholdsByWindow) +
        geom_errorbar(aes(ymin=onset.lower, ymax=onset.upper, x=year), width=.25) + 
        geom_point(aes(y=onset.median, x=year)) + 
        labs(x="RSV Season Onset")
    offset = ggplot(stateThresholdsByWindow) +
        geom_errorbar(aes(ymin=offset.lower, ymax=offset.upper, x=year), width=.25) + 
        geom_point(aes(y=offset.median, x=year)) + 
        labs(x="RSV Season Offset")

    ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
@

\caption{RSV season onset and offset by three-year superseason.}
\label{fig:onsetOffsetByYear}
\end{figure*}

\subsection{RSV season in low-incidence counties begins late}

\subsection{AAP guidelines perform best in low-incidence counties and worst in Fairfield county}

The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, which shows temporal misalignment between the time window of the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of AAP prophylaxis guidelines. Fairfield county, owing to its early season onset, has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.

\subsection{Spatially-informed regimens are superior to AAP recommendations overall and in Hartford county}

@@

\subsection{RSV season onset and offset is unchanged over time}

@@

\subsection{Recent-years prophylaxis regimens are non-superior to others.}

@@

Our model shows that coverage of RSV immunoprophylaxis in high-risk infants in Connecticut can be improved from that provided by the prophylaxis regimen currently recommended by the AAP.

@@

%\end{multicols}

>>>>

<<options, echo=FALSE>>=
    opts_chunk$set(echo=FALSE, message=FALSE, root.dir=".texpadtmp")
@

<<load>>=
read_chunk("../Analysis/RSV.R")
read_chunk("../Thesis/Thesis.R")
@

@@

<<util>>=
@

\documentclass[10pt,a4paper,draft]{article}

\usepackage{multicol,float}
\floatplacement{figure}{H}

\usepackage{printlen}
\usepackage{textcomp}

\usepackage{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
\usepackage{draftwatermark}
\SetWatermarkScale{1}
\SetWatermarkAngle{45}
\SetWatermarkFontSize{4ex}
\SetWatermarkHorCenter{12ex}
\SetWatermarkVerCenter{12ex}
\SetWatermarkLightness{.5}
\SetWatermarkText{DRAFT 2}

\input{structure.tex}

\usepackage[bf,medium,raggedright,compact]{titlesec}
\titleformat{\section}{\normalfont\large\bfseries\scshape}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize\bfseries\scshape}{}{0em}{}
\titleformat{\paragraph}{\normalfont\normalsize\bfseries}{}{0em}{}
\titlespacing*{\paragraph}{0pt}{3.25ex plus 1ex minus .2ex}{0em}

\newcommand{\abstractsection}[1]{\makebox[1in][l]{\textbf{#1}}}

\title{Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations}
\def\headertitle{Optimization of RSV prophylaxis using a generalized additive model of Connecticut hospitalizations}

\author{
    \authorstyle{Ben Artin\textsuperscript{1}}
    \newline\newline
    \authorstyle{Daniel Weinberger, PhD\textsuperscript{2}, advisor}\\
    \authorstyle{Virginia Pitzer, ScD\textsuperscript{2}, advisor}
    \newline\newline
    \textsuperscript{1}\institution{Yale University, School of Public Health and School of Medicine}\\
    \textsuperscript{2}\institution{Yale University, School of Public Health}
}

\date{\today}

@@

\begingroup
\setlength\parindent{0em}

@@

\clearpage
\endgroup

@@

\abstractsection{Background} Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants. Immunoprophylaxis (palivizumab) is available, but costly. The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season. Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunprophylaxis regimen outside of Florida.

\abstractsection{Methods} We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines. We also formulate several alternate immunoprophylaxis regimens with the same net pharmaceutical cost, estimate the fraction preventable by those alternate regimens.

\abstractsection{Results} At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions. We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens. Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% state-wide increase in RSV prophylaxis coverage over the AAP regimen.

\abstractsection{Conclusion} We conclude that the increased prophylaxis coverage provided by regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost. Our temporal analysis at the annual level showed no additional benefit beyond the spatial analysis, while simultaneously increasing implementation complexity. Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.

@@

\thispagestyle{empty}
\clearpage

\begin{multicols}{2}

@@

\subsection{Data normalization}

@@

\paragraph{RSV season in Fairfield county begins early and ends late}

@@

% \uselengthunit{in}\printlength{\columnwidth}
% column width = 3.20929 in

\begin{figure}
<<seasonByRegion, results='hide'>>=
    data = thresholdsByCounty %>% 
        filter(county %in% countiesForPlots) %>%
        melt(id=c("county")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
        cast(county + variable ~ pctile)

    tikz("figure/seasonByRegion.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(data) +
        theme_light(base_size=10) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
        geom_point(aes(y=median, x=county)) + 
        labs(aes(x=variable)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
        labs(y="Surveillance week") + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
        )
    dev.off()
@
\begin{center}
\input{figure/seasonByRegion.tex}
\caption{Onset and offset of RSV season in Connecticut by region}
\label{fig:seasonByRegion}
\end{center}
\end{figure}

\paragraph{RSV season in low-incidence counties begins late}

\paragraph{AAP guidelines perform best in low-incidence counties and worst in Fairfield county}

\begin{figure}
<<coverageByRegionAAP, results='hide'>>=
    tikz("figure/coverageByRegionAAP.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(unprotectedByCounty %>% filter(strat=="aap") %>% filter(county %in% countiesForPlots)) +
        theme_light(base_size=10) +
        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
        geom_point(aes(y=frac.median, x=county)) + 
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        labs(y="Preventable fraction") +
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank()
        )
    dev.off()
@
\input{figure/coverageByRegionAAP.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region.}
\label{fig:coverageByRegionAAP}
\end{figure}

The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}; temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of AAP prophylaxis regimen. Fairfield county, owing to its early season onset, has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.

\begin{figure}
<<coverageByRegionAAPInsight, results='hide'>>=
    tikz("figure/coverageByRegionAAPInsight.tex", width=plotWidth, height=plotHeight*3/2, pointsize=10)
    ggplot2.multiplot(plotlist=lapply(countiesForPlots, function(c) {
        strat = ppxFixedStrategies("all")[["aap"]]

@@

        plot = ggplot(countyPred) +
            geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25))
        plot = plot %>%
            annotation_timespan(ppxStart, ppxEnd, 1.05, hsv(1/3, 1, .5), "Prophylaxis") %>%
            annotation_timespan(countyThresholds$onset.median, countyThresholds$offset.median, -0.05, hsv(0, 1, .5), "RSV Season")
        plot = plot + 
            annotate("segment", x=-Inf, y=unprotectedAtStart, xend=ppxStart, yend=unprotectedAtStart, linetype=3) + 
            annotate("segment", x=-Inf, y=unprotectedAtEnd, xend=ppxEnd, yend=unprotectedAtEnd, linetype=3) + 
            scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.2, 0)) +
            labs(x=c) +
            theme(
                axis.title.y=element_blank(),
                axis.ticks.x=element_blank()
            )
        table = ggplot_gtable(ggplot_build(plot))
        table$layout$clip[table$layout$name == "panel"] <- "off"

        plot
    }), cols=2)
    dev.off()
@
\input{figure/coverageByRegionAAPInsight.tex}
\caption{RSV relative cumulative incidence by region}
\label{fig:coverageByRegionAAPInsight}
\end{figure}

\paragraph{Spatially-informed regimens are superior to AAP recommendations overall and in Hartford county}

@@

\begin{figure}
<<coverageByRegion, results='hide', warning=FALSE>>=
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots)
    tikz("figure/coverageByRegionRegimen.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(data) +
        theme_light(base_size=10) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_linetype_manual(values=c(1, 3, 4, 2, 3, 4, 2)) + 
        scale_color_manual(values=c(grey(0), rep(hsv(0, 1, 1), 3), rep(hsv(4/6, 1, 1), 3))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, linetype=strat, color=strat, group=strat), 
            width=0, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5)) +
        geom_point(aes(y=frac.lower, x=county, color=strat), position=position_dodge(.5), shape=18) +
        geom_point(aes(y=frac.upper, x=county, color=strat), position=position_dodge(.5), shape=18) +
        labs(y="Preventable fraction") +
        guides(color=guide_legend(keywidth=3, keyheight=1), linetype=guide_legend(keywidth=3, keyheight=1)) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@
\input{figure/coverageByRegionRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen.}
\label{fig:coverageByRegionRegimen}
\end{figure}

\paragraph{RSV season onset and offset are unchanged over time}

@@

\begin{figure}
<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    data = stateThresholdsByWindow %>% 
        melt(id=c("year")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
        cast(year + variable ~ pctile)

    tikz("figure/onsetOffsetByYear.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(data) +
        theme_light(base_size=10) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=year), width=.1) + 
        geom_point(aes(y=median, x=year)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLebeller) +
        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
        labs(y="Surveillance week") + 
        theme(
            axis.title.x=element_blank()
        )

    dev.off()
@
\input{figure/onsetOffsetByYear.tex}
\caption{RSV season onset and offset by three-year superseason.}
\label{fig:onsetOffsetByYear}
\end{figure}

\paragraph{Recent-years prophylaxis regimens are non-superior to others.}

@@

Our model shows that fraction of RSV preventable by immunoprophylaxis in high-risk infants in Connecticut can be increased from that of the prophylaxis regimen currently recommended by the AAP.

@@

\end{multicols}
